Distinguishing Between Spin-Aligned and Isotropic Binary Black Hole Populations Using Gravitational Wave Observations

### 2017-03-28 paper/AlignedIsotropicGW.tex
Added waveform systematics paper to references and moved w.f. systematics discussion to appendix.

Following the detection of a merging \ac{BBH} system, \ac{PE} tools
\citep{2015PhRvD..91d2003V} compare model gravitational waveforms
\citep{2014PhRvD..89h4006P,2014PhRvD..89f1502T,2014PhRvL.113o1101H}
against the observed data to obtain a posterior distribution on the
parameter space that describes the compact binary source.  The model
waveforms incorporate approximations to the true behaviour of the
merging systems that are expected to break down for sufficiently high
mis-aligned spins; detailed comparisons with numerical relativity
computations using no approximations to the dynamics
\citep{2016PhRvD..94f4035A} show no evidence of such a breakdown in
GW150914's analysis.  Given the preference of our data for smaller
spins (discussed below) we assume here that measurements made now and
in the future are not dominated by systematic errors.

@@

>>>>

Following the detection of a merging \ac{BBH} system, \ac{PE} tools
\citep{2015PhRvD..91d2003V} compare model gravitational waveforms
\citep{2014PhRvD..89h4006P,2014PhRvD..89f1502T,2014PhRvL.113o1101H}
against the observed data to obtain a posterior distribution on the
parameter space that describes the compact binary source.

@@

\section{Approximaions in the Gravitational Waveform}
The model waveforms used to infer the $\chieff$ of the three events
incorporate approximations to the true behaviour of the merging
systems that are expected to break down for sufficiently high
mis-aligned spins.  The effect of these approximations has been
investigated in detail for the inference on the parameters describing
GW150914 \citep{2016arXiv161107531T}.  For this source, statistical
uncertainties dominate over any waveform systematics.  Detailed
comparisons with numerical relativity computations using no
approximations to the dynamics \citep{2016PhRvD..94f4035A} also
suggest that statistical uncertainties dominate the systematics for
this system.  \citet{2016arXiv161107531T} suggests that systematics
may dominate for signals with this large SNR ($\simeq 23$) when the
source is edge-on or with high spin.  The other two events discussed
in this paper are at much lower SNR, with correspondingly larger
statistical uncertainties, and are probably similarly oriented and
with similarly small spins, so we do not expect systematic
uncertanties to dominate.

Given the preference of our data for a smaller spin population we
assume here that measurements made in the future are not dominated by
systematic errors, but this assumption would need to be revisited for
high-SNR, edge-on, or high-spin sources detected in the future.
